
---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---



## Loading and preprocessing the data
Set the working directory where the activity file is stored and read it
```{r}
setwd("C:/Users/s.maramreddy/OneDrive - Accenture/Personal/R/RepData_PeerAssessment1/activity")
activityfile <- read.csv("activity.csv")
```


## What is mean total number of steps taken per day?
```{r}
stepsum <- aggregate(steps~date, activityfile, sum)
hist(stepsum[,2])

mean(stepsum$steps)
median(stepsum$steps)
```

## What is the average daily activity pattern?
```{r}
stepsInterval <- aggregate(steps ~ interval, activityfile, mean, na.rm = TRUE)
plot(steps ~ interval, data = stepsInterval, type = "l")
stepsInterval[which.max(stepsInterval$steps), ]$interval
```


## Imputing missing values
Impute the missing values manually by calculating the mean of all the steps and then converting it to integer value

```{r}
missingval <- sum(!complete.cases(activityfile))
missingval

newfile <- activityfile
newfile$steps[is.na(newfile$steps)] <- as.integer(mean(newfile$steps, na.rm = T))
stepsum1 <- aggregate(steps~date, newfile, sum)
hist(stepsum1$steps)
mean(stepsum1$steps)
median(stepsum1$steps)
```

## Are there differences in activity patterns between weekdays and weekends?
```{r}
newfile$day = ifelse(as.POSIXlt(as.Date(newfile$date))$wday%%6 == 
    0, "weekend", "weekday")
# For Sunday and Saturday : weekend, Other days : weekday
newfile$day = factor(newfile$day, levels = c("weekday", "weekend"))
stepsInterval2 = aggregate(steps ~ interval + day, newfile, mean)

library(lattice)
xyplot(steps ~ interval | factor(day), data = stepsInterval2, aspect = 1/2, 
    type = "l")
```
During the weekday, there are more steps between the intervls 500-1000 where as weekend has more steps between intervals of 1000 - 2000
